---
output: github_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

STAMP Subset Testing and Analysis of Multiple Phenotypes
========================================================

Version 0.0

Authors: Andriy Derkach, Ruth Pfeiffer

Maintainer: Andriy Derkach (andriy.derkach@nih.gov)

Description:  We develop a flexible procedure (STAMP) based on mixture models to perform region based meta-analysis of different phenotypes using data from different GWAS and identify subsets of associated phenotypes. To run variance-component (quadratic test) under mixture model use mixtureQuad.r and mixtureLinear.r to run for burden (linear) tests.

Depndens:
  R (>= 3.2.1),
  psych,
  pscl,
  optimx,
  nleqslv,
  mvnfast,
  CompQuadForm

Installation
------------

Use [devtools](https://github.com/hadley/devtools) to install:

```R
library(devtools)
install_github("matt-sutton/STAMP") #Update gitrepo after pull request
```
Example Usage 
--------------
Import example
```{r}
library(STAMP)
data(Example_SC11)
names(Example_SC11)
length(Example_SC11$ListBeta)
length(Example_SC11$ListBeta[[1]])
```

Run variance-component (quadratic test) under mixture model:
```R
mixtureQuad(1000,Example_SC11$ListBeta,Example_SC11$ListSE,Example_SC11$ListCor,Example_SC11$MafList)
```

